Evolving Motion Machines

### 2019-04-25 Final/paper.tex
Genotype structure finished.

The genotypical structure of agents is very similar to the phenotypical instantiation.
Agents are stored as 3-dimensional arrays with each index contain specific data about its corresponding atom.

@@

%different distance measurement (relative angle)
%different terrain types
%different evaluation point (center of mass)
\section{Conclusion}

>>>>

The genotypical structure of agents is very similar to the phenotypical instantiation.
Agents are stored as 3-dimensional arrays with each index containing specific data about its corresponding atom.
Each atom is stored as a simple collection of four values; 
two integers for the shape and motion types, a float for the motion's force, and a vector containing the rotation direction.

Agents are structured this way partly because it makes serialization and deserialization simpler.
Serialization of agents converts the array of atoms into one long string.
First, atoms are serialized using Unity's built in serialization tools which simply convert the four fields described above into json format.
The array is then flattened to a 1-dimensional equivalent.
Each atom's json representation is then added to the agent's total serialized format, using semicolons to delimit the json strings.
Deserialization simply reverses this process, retrieving the necessary information for each atom from the serialized string.

The major reason for structuring agent's this way is that it is simpler to create the phenotype given this representation.
Stored as an array, detecting conflicting atoms is as simple as checking the index in question.
This is crucial for agents that modify their own structure, as is outlined in 2.3.
It is also a very simple representation to work with, although it does require more space than is aboslutely necessary.
However, alternative approaches to indexing spaces in the array that also determine conflicting neighbours in 3-dimensions adds unnecessary complexity to the structure.

Within the array, atoms are joined in a tree-based structure.
Each agent has exactly one atom that is not joined to a parent atom, essentially creating a root node.
This root node can then be joined to each atom in its von Neumann neighbourhood.
The joints used work similarly to ball and socket joints, allowing full rotation around any axis but keeping distance between each atom constant.
In this way, a \textit{parent} atom applies rotational force to its \textit{child} atoms, but not vice versa.
This tree structure acyclically joins all atoms together, creating a single large agent.

@@

%different distance measurement (relative angle)
%different terrain types
%different evaluation point (center of mass)
%cyclic joints in agent structure.
\section{Conclusion}
